### 2024-01-31 parts/transducers.tex
adding a small cojnecture
adding polyblind?

@@

>>>>

\subsection{Polyblind functions}

We are going to prove that polyblind functions are essentially
commutative.

\AP Given $q,k \in \Nat$, we define $\MSO^q_k$ to be the collection of types of
tuples of at most $k$ variables using quantifier rank at most $q$. We extend
the notation to a function $\MSO^q_k (u)$ that assigns to a word $u$ the number
of representative for each type.

\begin{lemma}
    Let $q \in \Nat$. The image
    $\MSO^q_1(\Sigma^*)$ is a semilinear set.
\end{lemma}
\begin{proof}
    Here is a context-free grammar that enumerates words
    in $\Sigma^*$ with letters colored by their $\MSO^q_1$ type.
    The initial non-terminal decides the global $\MSO^q$ type of the word,
    and given a non-terminal with an $\MSO^q$-type, we can split it in three
    by choosing a letter $a \in \Sigma$, an $\MSO^q$-type for the left,
    and an $\MSO^q$-type for the right, so that the types are coherent.
    We just have to remember the $\MSO^q$ type of the left and right
    of the current non-terminal to do that properly.

    By the Parikh’s theorem, the image of this is a semilinear set, that
    precisely computes $\MSO^q_1(\Sigma^*)$.
\end{proof}

\AP
Recall that a \intro{polyblind function} is a function such that.

\begin{lemma}
    Let $f \colon \Sigma^* \to \Rel$ be a \kl{polyblind function}.
    Then, there exists a computable function $g \colon \Nat^p \to \Rel$,
    that is \kl{commutative} and such that.
\end{lemma}

\AP
Look at the image of $\MSO^q_k$, is it semi-algebraic instead of semi-linear?
\begin{lemma}
    $\MSO^q_k(\Sigma^*)$ is a set of tuples that is obtained as a finite union 
    images of polynomials?
\end{lemma}

\subsection{}

@@

\begin{conjecture}
    Let $q,k \in \Nat$.
    Associate to a word $w$ the number of representatives
    of every $\MSO(q,k)$ type. 
    The image of this map is a semilinear set.
    In particular, it has a simple basis.
\end{conjecture}
